Stage-Splitting a Modal Language

### 2014-06-20 paper/semantics.tex
Finished up the example.
I had to add the prevs back in, making it stage 2.  Sorry, Kayvon.

Achieving this behavior mechanically requires us to resolve a contradiction:
we must substitute for \texttt{x} at stage \bbone, but we cannot evaluate inside the
$\next$ block bound to it. Our solution is to replace the $\next$ with a new variable and create an
explicit substitution (shown with a $\mapsto$) binding that variable to the $\next$'s contents.  
This substitution then floats up to the top of the containing $\prev$ block:
\begin{lstlisting} 
[y|->1+2]
let x = (yhat, 7) in
next{ prev{#1 x} * prev{#1 x} * prev{hold (#2 x)} }
\end{lstlisting}
Note that the variable left behind is rendered with a hat.  By treating this {\em hatted variable} as a value, we're now free to perform the stage-\bbone~substitution for {\tt x}.  
\begin{lstlisting} 
[x1|->1+2]
next{
	prev{#1 (yhat, 7)} *
	prev{#1 (yhat, 7)} *
	prev{hold (#2 (next{x1}, 7))}
}
\end{lstlisting}
To evaluate the remaining $\next$, we must first partially evaluate the body by finding all of the contained stage-\bbone~terms and reducing them:
\begin{lstlisting} 
[x1|->1+2]
	next{ x1 * x1 * 7 }
\end{lstlisting}
The final step in evaluating the outer $\prev$ is reifying the contained substitutions into let statements, yielding
\begin{lstlisting} 
let x1 = 1+2 in
  x1 * x1 * 7
\end{lstlisting}

Once again, the point here is that we did not duplicate the $1+2$ in our residual.  
Instead we lifted it out into a substitution, leaving a hatted variable [\TODO add hats above] in its place,
and we reified the substitution into a let-binding at the enclosing $\prev$.

>>>>

Achieving this behavior mechanically requires us to resolve a contradiction:
we must substitute for \texttt{x} at stage \bbone, but we cannot evaluate inside the $\next$ block bound to it. 
Our solution is to replace the $\next$ with a new variable and create an explicit substitution (shown with a $\mapsto$) binding that variable to the $\next$'s contents.  
This substitution then floats up to the top of the containing $\prev$ block:
\begin{lstlisting} 
prev {
[y|->1+2]
  let x = (yhat, 7) in
  next{prev{#1 x} * prev{#1 x} * prev{hold (#2 x)}}
}
\end{lstlisting}
Note that the variable left behind is rendered with a hat.  By treating this {\em hatted variable} as a value, we're now free to perform the stage-\bbone~substitution for {\tt x}.  
\begin{lstlisting} 
prev {
[y|->1+2]
  next{
    prev{#1 (yhat, 7)} * prev{#1 (yhat, 7)} *
    prev{hold (#2 (yhat, 7))}
  }
}
\end{lstlisting}
To evaluate the remaining $\next$, we must first partially evaluate the body by finding all of the contained stage-\bbone~terms and reducing them. 
As a rule, these will reduce to hatted variables, and $\prev$ removes the hat, leaving the variable in place:
\begin{lstlisting} 
prev {
[y|->1+2]
    next{ y * y * 7 }
}
\end{lstlisting}
Once again, we lift the contents of the $\next$ into a substitution:
\begin{lstlisting} 
prev {
[y|->1+2]
[z|->y*y*7]
    zhat
}
\end{lstlisting}
Finally, when evaluating the outer $\prev$, we must {\em reify} the contained substitutions into let statements, yielding
\begin{lstlisting} 
let y = 1+2 in
let z = y * y * 7 in z
\end{lstlisting}

Thus we have evaluated all of the stage \bbone\ expressions of this program without duplicating the contents of $\next$ blocks.
